---
execute:
    echo: false
    warning: false
---

# PATIENT_VACCINE_DEFERRAL {.unnumbered}

```{r,eval=TRUE,echo=FALSE}
#| label: source-filefolder
dr <- "C:/Users/ajp5303/OneDrive - Washington State Executive Branch Agencies/source_scripts"
```

```{r,eval=TRUE,echo=FALSE}
#| label: source-files
source(paste0(dr,"/dbconnection.R"))
source(paste0(dr,"/dqguide_functions.R"))
```

## Description

The patient_vaccine_deferral table contains a list of patient record IDs and their associated deferral records. Details include the vaccine code, dose number, deferral date, and deferral reason.

## Columns

```{r}
#| label: ptvacdef-colnames
tibble(Columns = (tbl(synapse, in_schema("dbo", "H33_PATIENT_VACCINE_DEFERRAL")) %>% colnames()),
       Type = tbl(synapse, in_schema("dbo", "H33_PATIENT_VACCINE_DEFERRAL")) %>% head(1) %>% as_tibble() %>% sapply(class)
       ) %>%
 gt() %>%
 gt_theme_espn()
```

## Category Description

This section contains variable coding for relevant columns within the PATIENT_VACCINE_DEFERRAL table.

```{r}
#| label: tab-ptvacdef
vcvar_tabl <-
tibble(Coding = c(#top 10 iis vaccination code 
                  "921","75","2061","73","61","614","2033","31","2080","108"
                  
                  "ALTSCHEDULE","SHORTAGE","02","03","WAIT","ILLNESS","01","00", 
                  
                  #top 8 deferral reasons
                  
               
       Description = c(#iis vacc code descriptor
                     "Tdap","influenza, injectable, quadrivalent, preservative free","zoster recombinant","influenza, injectable, quadrivalent","Influenza, seasonal, injectable","Pneumococcal conjugate PCV 13","HPV9","pneumococcal polysaccharide PPV23","COVID-19, mRNA, LNP-S, PF, 100 mcg/0.5mL dose or 50 mcg/0.25mL dose","influenza, unspecified formulation"
                      
                       #deferral reasons descriptor
                      "Patient/Parent Chooses Alternate Schedule","Vaccine Shortage","Other","Patient Decision","Patient/Parent Chooses to Wait","Temporary Acute Illness","Religious exemption","Parental Decision"
                  
      Variable = c(#vaccination code category
                    "ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE",
                    
                    #deferral reasons 
                    "DEFERRAL_REASON","DEFERRAL_REASON","DEFERRAL_REASON","DEFERRAL_REASON","DEFERRAL_REASON",
                    
                    
      Space = " ") %>%
       gt(rowname_col = "Space", groupname_col = "Variable") %>%
       tab_header(title = "Variable Coding") %>%
       cols_width(Coding~px(200),
                  Description~px(600),
                  Space~px(150)) %>%
       cols_align(align = "left") %>%
       tab_footnote(
                    footnote = 
                      gt::md(paste0("A full list of IIS Vaccination Codes is available at: ",
                    {"[https://www2a.cdc.gov/vaccines/iis/iisstandards/?rpt=cpt](https://stateofwa.sharepoint.com/:x:/r/sites/DOH-oiinformatics/Shared%20Documents/CEDAR/CEDAR%20Data%20Dictionaries/ASIIS_Vacc_Code%20Values%20Table%20with%20CDC%20and%20CPT%20Codes.xlsx?d=w58a7246c67aa491fbfef19172d5ca393&csf=1&web=1&e=rIrViQ)"}
                    )),
                    locations = cells_row_groups(groups = "ASIIS_VACC_CODE")
       ) %>%
       gt_theme_espn()

ptvacdef_tabl
```


## Statistics

```{r}
#| label: ptvacdef-stats
tibble(columncnt = (tbl(synapse, in_schema("dbo", "H33_PATIENT_VACCINE_DEFERRAL")) %>% ncol()),
       rowcnt = (tbl(synapse, in_schema("dbo", "H33_PATIENT_VACCINE_DEFERRAL"))) %>% nrow2()
       ) %>%
  gt() %>%
  cols_label(columncnt = "Number of Columns",
             rowcnt = "Number of Rows")  %>%
  gt_theme_espn()
```
