---
execute:
    echo: false
    warning: false
---

# TRANSFER {.unnumbered}

```{r,eval=TRUE,echo=FALSE}
#| label: source-filefolder
dr <- "C:/Users/ajp5303/OneDrive - Washington State Executive Branch Agencies/source_scripts"
```

```{r,eval=TRUE,echo=FALSE}
#| label: source-files
source(paste0(dr,"/dbconnection.R"))
source(paste0(dr,"/dqguide_functions.R"))
```

## Description

Like the transfer_items table, the transfer table contains a list of transfer IDs and details associated with each transfer, including the status of the transfer, approving user, and receiving user. Key information on the reviewing user, including userID, approval or denial date of the transfer, is included.

## Columns

```{r}
#| label: transf-colnames
tibble(Columns = (tbl(synapse, in_schema("dbo", "H33_TRANSFER")) %>% colnames())) %>%
 mutate(Type = typeof(Columns)) %>%
 gt() %>%
 gt_theme_espn()
```

## Category Description

## Statistics

```{r}
#| label: transf-stats
tibble(columncnt = (tbl(synapse, in_schema("dbo", "H33_TRANSFER")) %>% ncol()),
       rowcnt = (tbl(synapse, in_schema("dbo", "H33_TRANSFER"))) %>% nrow2()
       ) %>%
  gt() %>%
  cols_label(columncnt = "Number of Columns",
             rowcnt = "Number of Rows")  %>%
  gt_theme_espn()
```

:::
