---
execute:
    echo: false
    warning: false
---

# VACCINE_PRODUCT {.unnumbered}

```{r,eval=TRUE,echo=FALSE}
#| label: source-filefolder
dr <- "C:/Users/ajp5303/OneDrive - Washington State Executive Branch Agencies/source_scripts"
```

```{r,eval=TRUE,echo=FALSE}
#| label: source-files
source(paste0(dr,"/dbconnection.R"))
source(paste0(dr,"/dqguide_functions.R"))
```

## Description

The vaccine_product table contains a list of vaccine product IDs and their corresponding ASIIS_VACC_CODE values. This table also contains a description and the maker of the vaccine product.

## Columns

```{r}
#| label: vaccprod-colnames
tibble(Columns = (tbl(synapse, in_schema("dbo", "H33_VACCINE_PRODUCT")) %>% colnames()),
       Type = tbl(synapse, in_schema("dbo", "H33_VACCINE_PRODUCT")) %>% head(1) %>% as_tibble() %>% sapply(class)
  ) %>%
  gt() %>%
  gt_theme_espn()
```

## Category Description

This section contains variable coding for relevant columns within the VACCINE_PRODUCT table.

```{r}
#| label: tab-vaccprod
vaccprod_tabl <-
tibble(Coding = c(#top 5 iis vaccination code 
                  "3036","75","3035","2070","2041"), 
                      
              
       Description = c(#iis vacc code descriptor
                      "COVID-19, mRNA, LNP-S, bivalent booster, PF, 30 mcg/0.3 mL dose", 
                      "influenza, injectable, quadrivalent, preservative free",
                      "COVID-19, mRNA, LNP-S, bivalent booster, PF, 50 mcg/0.5 mL or 25mcg/0.25 mL dose",
                      "influenza, high-dose, quadrivalent",
                      "Influenza, injectable, MDCK, preservative free, quadrivalent"), 
                               
      Variable = c(#vaccination code category
                    "ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE"),  
                    
      Space = " ") %>%
       gt(rowname_col = "Space", groupname_col = "Variable") %>%
       tab_header(title = "Variable Coding") %>%
       cols_width(Coding~px(200),
                  Description~px(600),
                  Space~px(150)) %>%
       cols_align(align = "left") %>%
       tab_footnote(
                    footnote = 
                      gt::md(paste0("A full list of commonly used IIS Vaccination Codes in WA is available at: ",
                    {"https://doh.wa.gov/sites/default/files/2022-02/348-580-ConsolidatedBestChoicesGuide.pdf"}
                    )),
                    locations = cells_row_groups(groups = "ASIIS_VACC_CODE")
       ) %>%
       gt_theme_espn()

vaccprod_tabl
```

## Statistics

```{r}
#| label: vaccprod-stats
tibble(columncnt = (tbl(synapse, in_schema("dbo", "H33_VACCINE_PRODUCT")) %>% ncol()),
       rowcnt = (tbl(synapse, in_schema("dbo", "H33_VACCINE_PRODUCT"))) %>% nrow2()
  ) %>%
  gt() %>%
  cols_label(columncnt = "Number of Columns",
             rowcnt = "Number of Rows")  %>%
  gt_theme_espn()
```

