---
execute:
    echo: false
    warning: false
---

# VACCINATION_MASTER {.unnumbered}

```{r,eval=TRUE,echo=FALSE}
#| label: source-filefolder
dr <- "C:/Users/ajp5303/OneDrive - Washington State Executive Branch Agencies/source_scripts"
```

```{r,eval=TRUE,echo=FALSE}
#| label: source-files
source(paste0(dr,"/dbconnection.R"))
source(paste0(dr,"/dqguide_functions.R"))
```

## Description

The vaccination_master table contains details on vaccination events, including vaccination code, facility and ordering provider, lot number, and manufacturer details.

## Columns

```{r}
#| label: vcmstr-colnames
tibble(Columns = (tbl(synapse, in_schema("dbo", "H33_VACCINATION_MASTER")) %>% colnames()),
       Type = tbl(synapse, in_schema("dbo", "H33_VACCINATION_MASTER")) %>% head(1) %>% as_tibble() %>% sapply(class)
       ) %>%
 gt() %>%
 gt_theme_espn()
```

## Category Description

```{r}
#| label: vcmstr-table
vcvar_tabl <-
tibble(Coding = c(#top 5 iis vaccination code 
                  "3036","75","3035","2070","2041", 
                  #full list in table cdc_to_asiis_vacc_code
                  
                  "300","150","229","197","171", #top 5 cdc vacc code 
                  #link to full url: https://www2a.cdc.gov/vaccines/iis/iisstandards/?rpt=cpt
                  
                  #top 5 cpt
                  "91312","90715","90686","90670","90750",  
                  #vacc code link to full url:   https://www2a.cdc.gov/vaccines/iis/iisstandards/vaccines.asp?rpt=cpt
                  
                  #top 15 manufacturer codes
                  "PFR","PMC","MOD","SEQ","SKB", "MSD","IDB","MSP","SP","BN","MBL","JSN","DVX","WAL","MED", 
                 # link to full url https://www2a.cdc.gov/vaccines/iis/iisstandards/vaccines.asp?rpt=mvx
                
                 "LD","RD","LVL","RVL","LLFA","RLFA", #coded terms for vaccination site
                 #full vocabulary set:
                 #https://phinvads.cdc.gov/vads/ViewValueSet.action?id=98257779-17B8-DF11-9BDD-0015173D1785
                
                 #adverse reaction codes
                 "26","42","44","48","46","51","32"),  
                 #data set in data dictionary - need to post to sharepoint
                  
            
       Description = c(#iis vacc code descriptor
                      "COVID-19, mRNA, LNP-S, bivalent booster, PF, 30 mcg/0.3 mL dose (CDC code 300)", 
                      "Influenza, injectable, quadrivalent, preservative free (CDC code 150)",
                      "COVID-19, mRNA, LNP-S, bivalent booster, PF, 50 mcg/0.5 mL or 25mcg/0.25 mL dose (CDC code 229)",
                      "influenza, high-dose seasonal, quadrivalent, preservative free (CDC code 197)",
                      "Influenza, injectable, Madin Darby Canine Kidney, preservative free, quadrivalent 
                      (CDC code 171)", 
                       
                       #cdc vacc code descriptor
                       "COVID-19, mRNA, LNP-S, bivalent booster, PF, 30 mcg/0.3 mL dose",
                       "Influenza, injectable, quadrivalent, preservative free",
                       "COVID-19, mRNA, LNP-S, bivalent booster, PF, 50 mcg/0.5 mL or 25mcg/0.25 mL dose", 
                       "Influenza, high-dose, quadrivalent",
                       "Influenza, injectable, MDCK, preservative free, quadrivalent", 
       
                       #cpt vacc code descriptor
                       "Pfizer™ COVID-19 Vaccine - Bivalent Booster, Gray Cap",
                       "Adacel™ Tdap Vaccine",
                       "Fluarix™ Influenza Vaccine",
                       "Prevnar 13™ Pneumococcal Vaccine",
                       "Shingrix™ Zoster Vaccine", 
                       
                       #manufacturer code descriptor
                       "Pfizer, Inc.",
                       "Sanofi Pasteur",
                       "Moderna US, Inc.",
                       "Seqirus",
                       "GlaxoSmithKline",
                       "Merck and Co., Inc.",
                       "ID Biomedical",
                       "MSP Vaccine Company - (partnership Merck and Sanofi Pasteur)",
                       "Assumed misscoded value for Sanofi Pasteur (PMC)",
                       "Bavarian Nordic A/S",
                       "Massachusetts Biologic Laboratories",
                       "Janssen",
                       "Dynavax, Inc.",
                       "Wyeth",
                       "MedImmune, Inc. (AstraZeneca)",
       
       
                        #anatomical site descriptor
                        "Left Deltoid",
                        "Right Deltoid",
                        "Left Vastus Lateralis",
                        "Right Vastus Lateralis",
                        "Left Lower Forearm",
                        "Right Lower Forearm",
                        
                        #adverse reaction code descriptor
                        "Other",
                        "Vasovagal syncope (7 days)",
                        "Life threatening adverse event",
                        "An important medical event that based on appropriate medical judgement may jeopardize the
                         individual and may require medical or surgical intervention",
                        "Persistent or significant incapacity or substantial disruption of the ability to 
                         conduct normal life functions",
                        "Serious Adverse Event regardless of causality",
                        "Any acute complications or sequelae (including death) of above events 
                         (interval - not applicable)"),
       
      Variable = c(#vaccination code category
                    "ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE","ASIIS_VACC_CODE",
                    
                    #cdc vacc category
                    "CDC_VACC_CODE","CDC_VACC_CODE","CDC_VACC_CODE","CDC_VACC_CODE","CDC_VACC_CODE",
                    
                    #cpt category
                    "CPT_VACC_CODE","CPT_VACC_CODE","CPT_VACC_CODE","CPT_VACC_CODE","CPT_VACC_CODE", 
                    
                    #manufacturer category
                    "manufacturer","manufacturer","manufacturer","manufacturer","manufacturer","manufacturer",
                    "manufacturer","manufacturer","manufacturer","manufacturer","manufacturer","manufacturer",
                    "manufacturer","manufacturer","manufacturer",
       
                    #anatomical site category
                    "anatomical_site","anatomical_site","anatomical_site","anatomical_site","anatomical_site",
                    "anatomical_site","anatomical_site",
                    
                    #adverse reaction code category
                    "adverse_reaction","adverse_reaction","adverse_reaction","adverse_reaction","adverse_reaction",
                    "adverse_reaction"),
       
      Space = " ") %>%
       gt(rowname_col = "Space", groupname_col = "Variable") %>%
       tab_header(title = "Variable Coding") %>%
       cols_width(Coding~px(200),
                  Description~px(600),
                  Space~px(150)) %>%
       cols_align(align = "left") %>%
       tab_footnote(
                    footnote = 
                      gt::md(paste0("A full list of CDC Vaccination Codes is available at: ",
                    {"https://www2a.cdc.gov/vaccines/iis/iisstandards/?rpt=cpt"}
                    )),
                    locations = cells_row_groups(groups = "CDC_VACC_CODE")
       ) %>%
       tab_footnote(
                    footnote = 
                      gt::md(paste0("A full list of Vaccination CPT Codes is available at: ",
                    {"https://www2a.cdc.gov/vaccines/iis/iisstandards/vaccines.asp?rpt=cpt"}
                    )),
                    locations = cells_row_groups(groups = "CPT_VACC_CODE")
       ) %>%
       tab_footnote(
                    footnote = 
                      gt::md(paste0("A full list of Vaccine Manufacter Codes is available at: ",
                    {"https://www2a.cdc.gov/vaccines/iis/iisstandards/vaccines.asp?rpt=mvx"}
                    )),
                    locations = cells_row_groups(groups = "manufacturer")
       ) %>%
       tab_footnote(
                    footnote = 
                      gt::md(paste0("A full vocabulary list of coded terms for vaccination sites is available at: ",
                    {"https://phinvads.cdc.gov/vads/ViewValueSet.action?id=98257779-17B8-DF11-9BDD-0015173D1785"}
                    )),
                    locations = cells_row_groups(groups = "anatomical_site")
       ) %>%
       gt_theme_espn()

vcvar_tabl
```

```{r}
vaccmstrode <- tibble(
  Codes = c("CDC Vaccination Codes", "Vaccination CPT Codes","Vaccine Manufacter Codes","Vaccination Sites"),
  Links = c("https://www2a.cdc.gov/vaccines/iis/iisstandards/?rpt=cpt",
           "https://www2a.cdc.gov/vaccines/iis/iisstandards/vaccines.asp?rpt=cpt",
           "https://www2a.cdc.gov/vaccines/iis/iisstandards/vaccines.asp?rpt=mvx",
           "https://phinvads.cdc.gov/vads/ViewValueSet.action?id=98257779-17B8-DF11-9BDD-0015173D1785")
)

vacmstrcode_tab <- vaccmstrode %>%
  mutate(Links = sprintf('<p><a href = "%s">%s</a>', Links, Links), 
         Links = map(Links, gt::html)) %>%
  gt() %>%
  tab_header(title = "Full Code Lists for Vaccine Master Table") %>%
  cols_align(align = "left") %>%
  cols_width(Codes~px(200),
             Links~px(800)) %>%
  gt_theme_espn()

vacmstrcode_tab
```

## Statistics

15.59% of records have a CDC_VACC_CODE value of "217" (COVID-19, mRNA, LNP-S, PF, 30 mcg/0.3 mL dose, tris-sucrose).

20.26% of records list the primary manufacturer as Pfizer, Inc. 21.34% of records did not have a manufacturer value \[null\].

86.67% of records have no CPT_VACC_CODE value reported \[null\]. The most frequently reported CPT value is 90715 at 1.66%.

The most frequently occurring value for AIIS_VACC_CODE is "3015" (11.32%) followed by "2080" (10.86%) Note: The above statistics include cases with a vacc_date value between 1/1/22 and 11/1/22.

```{r}
#| label: vcmstr-stats
tibble(columncnt = (tbl(synapse, in_schema("dbo", "H33_VACCINATION_MASTER")) %>% ncol()),
       rowcnt = (tbl(synapse, in_schema("dbo", "H33_VACCINATION_MASTER"))) %>% nrow2()
       ) %>%
  gt() %>%
  cols_label(columncnt = "Number of Columns",
             rowcnt = "Number of Rows")  %>%
  gt_theme_espn()
```
